---
title: "p8105_hw1_zz3168"
author: "Zixuan Zhang"
date: "2023-09-20"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Problem 0.1
```{r}
library(moderndive)
```

# Problem 1
```{r}
data("early_january_weather")
early_january_weather
```
In `early_january_weather` dataset contains information on weather conditions.

```{r}
nrow(early_january_weather)
ncol(early_january_weather)
mean(early_january_weather$temp)
```

the data set consists of `r nrow(early_january_weather)` rows and `r ncol(early_january_weather)` columns, and the The mean temperature in this dataset is `r mean(early_january_weather$temp)` degrees.


#Make a scatterplot
```{r}
library(tidyverse)
ggplot(early_january_weather, 
       aes(x = time_hour,
           y = temp,
           color = humid
           )
       )+ geom_point() 
  
  ggsave("scatterplot.pdf")
```

# Problem 2

#create a data frames
```{r}
AA_data_frame = tibble(
  vec_numeric = rnorm(10),
  vec_char = letters[1:10],
  vec_logical =  vec_numeric > 0,
  vec_factor = factor(c("1","2","3","4","5","6","7","8","9","10"))
)
```

#pull

```{r}
library(tidyverse)
AA_data_frame_mean = mean(pull(AA_data_frame, vec_numeric))
vec_char_mean = mean(pull(AA_data_frame, vec_char))
#This will cause error
vec_logical_mean = mean(pull(AA_data_frame, vec_logical))
vec_factor_mean = mean(pull(AA_data_frame, vec_factor))
#This will cause error
```
So the mean in the `vec_numeric` and `vec_logical` is work and the other two will cause error, because we cannot use `vec_char` and `vec_factor` to calculate mean.


#Convert logical to numeric
```{r}

```

